### 2019-08-01 README.Rmd
rework vignette building

A short video showing the task can be found under [`img/vignettes/santa_task_example.mp4`](https://github.com/richarddmorey/Morey_Hoekstra_StatCognition/blob/master/vignettes/img/santa_task_example.mp4)  (click 'View raw' to download).

>>>>

A short video showing the task can be found under [`inst/manuscript/img/santa_task_example.mp4`](https://github.com/richarddmorey/Morey_Hoekstra_StatCognition/blob/master/inst/manuscript/img/santa_task_example.mp4)  (click 'View raw' to download).
